Interactive Visualization of Hierarchically Structured Data

### 2016-12-06 treelapse.Rmd
Make yaml compatible with jcgs template

---
title: "Interactive Visualization of Hierarchically Structured Data"
author: "Kris Sankaran and Susan Holmes"
date: "`r Sys.Date()`"
output:
    bookdown::pdf_book:
        toc: false
bibliography: ["bibliography.bib"]
biblio-style: "agsm"
link-citations: yes
---

>>>>

---
author: "Kris Sankaran and Susan Holmes"
date: "`r Sys.Date()`"
standalone: true
documentclass: article
fontsize: 12pt
output:
  bookdown::pdf_book:
    keep_tex: yes
    toc: false
    includes:
      in_header: preamble.tex
      before_body: before_body.tex
bibliography: ["bibliography.bib"]
biblio-style: "agsm"
link-citations: yes
---
